\LARGE \bf Bringing robotics in formal education \\ using the Thymio open source hardware robot

### 2016-04-09 paper_ram.tex
small type

Our main concern during the mechatronic design of Thymio was to keep a low production cost. 
Price is a key factor for the adoption of the robot by schools~\cite{kradolfer2014sociological}.
In our previous experience with designing robots, most of the costs was due to the electronics and the sensors~\cite{thesis_michael}, not to the mechanical parts.
As we wanted Thymio to be an affordable robot, we selected electronic components with great care and explored different design solutions in order to limit the number of expensive components.
In particular, we focused on low-cost sensors that allow rich interaction possibilities, with both the environment and the user.
The resulting Thymio robot possesses a large number of sensors:
Seven horizontal infrared distance sensors, with a range of about 13\,cm.
They enable many interactions with the environment, like following an object or avoiding an obstacle.
Two ground infrared sensors allow to follow a line or to detect the edge of a table.
A three-axis accelerometer measures the orientation of the robot with respect to gravity, and can detect shocks and free falls.
Five capacitive touch buttons organized as an arrow form an intuitive user interface.
Compared to physical buttons, these simplify the plastic hull of the robot and make it more robust.
A remote control receiver provides additional distant buttons.
A microphone can record sounds and detect claps. 
Finally, a thermistor measures temperature.
Most of these sensors cost less then 0.2\,\$, the most expensive being the accelerometer with a cost of about 0.8\,\$, which is an acceptable price given the possibilities it brings to the robot.
%The omnipresence of this type of sensors in smartphones and compact cameras has drastically lowered their prices over the last decade.
We also chose low-cost toy motors and control them in speed (max. 13\,cm/s) using a custom-designed electronics.
By measuring the back-electromotive force, speed control is possible without additional encoders.

>>>>

Our main concern during the mechatronic design of Thymio was to keep a low production cost. 
Price is a key factor for the adoption of the robot by schools~\cite{kradolfer2014sociological}.
In our previous experience with designing robots, most of the costs were due to the electronics and the sensors~\cite{thesis_michael}, not to the mechanical parts.
As we wanted Thymio to be an affordable robot, we selected electronic components with great care and explored different design solutions in order to limit the number of expensive components.
In particular, we focused on low-cost sensors that allow rich interaction possibilities, with both the environment and the user.
The resulting Thymio robot possesses a large number of sensors:
Seven horizontal infrared distance sensors, with a range of about 13\,cm.
They enable many interactions with the environment, like following an object or avoiding an obstacle.
Two ground infrared sensors allow to follow a line or to detect the edge of a table.
A three-axis accelerometer measures the orientation of the robot with respect to gravity, and can detect shocks and free falls.
Five capacitive touch buttons organized as an arrow form an intuitive user interface.
Compared to physical buttons, these simplify the plastic hull of the robot and make it more robust.
A remote control receiver provides additional distant buttons.
A microphone can record sounds and detect claps. 
Finally, a thermistor measures temperature.
Most of these sensors cost less then 0.2\,\$, the most expensive being the accelerometer with a cost of about 0.8\,\$, which is an acceptable price given the possibilities it brings to the robot.
%The omnipresence of this type of sensors in smartphones and compact cameras has drastically lowered their prices over the last decade.
We also chose low-cost toy motors and control them in speed (max. 13\,cm/s) using a custom-designed electronics.
By measuring the back-electromotive force, speed control is possible without additional encoders.
